Probabilistic Inference of NYC Congestion from Taxi Data

### 2017-12-10 reports/paper/paper.tex
Added puzzles.

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figs/unifmaps.pdf}
\includegraphics[width=0.5\textwidth]{figs/softmaxmaps.pdf}
\caption{Learned Weights, Various Times Tuesday. Top Row: Uniform Model.
Bottom Row: Softmax Model.}
\label{fig:unifmap}
\end{figure}

@@

% chekcboard?
% bias?
% unclear how to decide which one is better
% improve the softmax one??
%

\begin{itemize}
\item What conclusions can you draw from the results section?
\item Is there further analysis you can do into the results of the system? Here is a good place to include visualizations, graphs, qualitative analysis of your results.

\end{itemize}

@@

%TODO

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{figs/unifmaps.pdf}
\includegraphics[width=0.5\textwidth]{figs/softmaxmaps.pdf}
\caption{Learned weights, various times Tuesday. Top row: uniform model.
Bottom row: softmax model.}
\label{fig:unifmap}
\end{figure}

@@

While many of our results make sense in the context of the models that produce
them, some puzzles---both qualitative and quantitative---remain. For instance,
visual inspection of the grid of weights that the softmax model converges to
(see bottom row of Figure \ref{fig:unifmap}) reveals a pattern that resembles a
checkerboard. This behavior is most visible in the 4:00 AM weights, but also
appears in certain areas of the other grids. We suspect this has to do with the
superimposition of paths that we train on, but the result largely remains an
unexpected surprise.

Furthermore, we are also intrigued by the bias our models introduce: both the
uniform and softmax structural models on average underestimate trip duration
(see Table \ref{tab:mainres}). Since we optimize an approximate bound, it
is believable that this procedure introduced bias. Nevertheless, we are
missing a good intuition as to why we systematically underestimate and whether
this is a feature or a bug.

\subsection{Future Work}

In thinking of ways to develop our work further, a couple of directions come to
mind. Foremost among them is taking a closer look at which of the softmax and
uniform models best captures reality. They perform very similarly on our
test data, but their weights correspond to structurally different maps of
Manhattan. Future work could help determine which of these depictions best
tracks actual traffic conditions.

In addition, our models currently train from scratch on each partition of the
data. However, it is not hard to imagine that, for example, traffic conditions
at 8:00 AM on Tuesdays can tell you something about conditions at 9:00 AM on
Tuesdays, or 8:00 AM on Wednesdays. Exploring ways to leverage this structure
through transfer learning could significantly speed up the training of our
models.

% checkboard?
% bias?
% unclear how to decide which one is better
% improve the softmax one??
% transfer learning from different times

% \begin{itemize}
% \item What conclusions can you draw from the results section?
% \item Is there further analysis you can do into the results of the system? Here is a good place to include visualizations, graphs, qualitative analysis of your results.
% 
% \end{itemize}

@@
